### 2016-07-05 sections/R10.0.tex

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One dimensional Self-organizing maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of the exploring M31 data with 1D maps is to monitor the general behaviour of data. 
    1D SOMs can have from the minimum number of clusters, $1\times2$, to the highest number of cluster possible.
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without the clustering the data.
    On the other hand, higher grid 1D SOMs are a helpful tool to get quick insight into data.
%    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
%Clustering
 %   \subsection{Clustering M31 data}

        In order to monitor how the data behaves, we created SOMs with two to fourteen neurons (Fig.~\ref{fig: M31_nets_1d}).
        The $1\times2$ network (Fig.~\ref{fig: M31_net_1by2}) shows how the M31 data can be divided into two broad categories.
        While the $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network that all the regions in M31 are completely separated.
        Since in the higher network sizes, regions have more space to be separated based on their differences, we can see that from $1\times2$ to $1\times14$ network the M31 regions separated from each other increasingly, until they are completely separated.

        In Fig.~\ref{fig: M31_net_1by2}, it is clear that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarity between two groups, but they are not very similar. 
        By increasing the size of the neurones to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that the region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between two left neurons suggests that regions, which occupy these neurons are very similar to each other, while the black colour between two right neurons expresses otherwise.

        %%%Talking about four right regions
        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAH flux intensity compare to other regions (Fig. 5 in \cite{Dim15}). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensity in all the MIR and FIR bands, and have high dust luminosity and dust mass.
        The higher values in these values could be the reason that these 4 regions become separated from the others, in $1\times2$ network.
        Besides, Regions 1, and 9 are in the 10~Kpc ring, region 2 is slightly out of the 10~Kpc ring and the region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason of regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        The similarity in the other input values with the other regions causes regions 1, 2, and 9 gradually move towards other regions, and have more distance with region 10, in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

@@

        \begin{figure}
            \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
             }
            \hfill
            \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
            \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
             }
             \hfill
            \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
             }%%% What should I do with this one! It doesn't look good visually
            \caption{SOM of the M31 data from $1\times2$~, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple Hexagonal shapes represent the neurons. The grey cycle colours show the differences between weight of each neuron with white is the minimum differences and black has the maximum one. The numbers in the plot show the regions that are located in each neuron.}
            \label{fig: M31_nets_1d}
        \end{figure}

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network, that has no neuron occupied by more than one region.
        In a higher grid SOM, network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all the 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar area in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely show more similarity to each other.
        In Fig.~\ref{fig: M31_net_1by14}, the most right neuron is occupied by region 10.
        Two black colour between this region and the others indicates the high differences between this neuron and the other ones.
        The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences from region 10.

    \subsection{Inside the 2 neuron network}%%% I will find better title for this subsection
        %What is going on in this section
        \label{sec: inside_the_2_neurons}
        Using SOMs, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other, for a reason.
        This reason can vary from having higher values in some specific wavelengths, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data, that cannot be seen in other groups or in a Galaxy as a whole.
        To investigate the later, we showed the Pearson correlation coefficients for the inputs from regions 3 to 8 in Fig.~\ref{fig: cor_cluster1}, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure}
        \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left side of the Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure}

        %%% what regions' version shows and how it compares with the other one:
        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features highly correlate with each other. 
        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
        However, in Fig.~\ref{fig: cor_cluster1}, 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most of the other quantities.
        The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between 12 and 12.7~$\mu$m PAH fluxes.
        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves.

        For the rest of the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity, neither.
        They have correlations with SPIRE emission, but they are weaker than the ones with data from all regions.
        Correlations between PAH features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
        Many groups used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier in data (Region 6). 
        When we disregard the outlier data, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\rm TIR}$) reappear.
        Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.

        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with amount of dust while \halpha~emission anti-correlate with amount of dust due to extinction \citep{Calzetti94}.
        Therefore,higher amount of PAH fluxes means higher amount of dust abundance and less \halpha~emission (The same for \sii~and \oiii~emission).
        Second, it is the effect of observing apertures.
        If the observed regions are located in the edge of the H {\sc II} regions we would expect too see more PAH and less \halpha~emission. %%% reference?
        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
        \cite{Wu06} discussed these ant-correlations could be the result of destruction of the PAH due to the high amount of harder radiation (thus higher RHI).
        On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAH features underlying continuum emission is from the H {\sc II} regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
        The later reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.

        The strong anti-correlation between PAHs and stellar mass shows, despite the general assumption that the one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Haas02,Bendo08,Calapa14, Lu14,Jones15}, the higher stellar mass decreases PAH emission.
        Using M33 data,~\cite{Calapa14} showed that 8/250~$\mu$m luminosity ratio correlate with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
        In Fig.~\ref{fig: cor_cluster1}, we see a week anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
        We couldn't see any correlation between 8/250~$\mu$m luminosity and stellar mass, neither in clustered data nor in all 10 regions.
      %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
      %It is possible that all the 10 regions in M31 simply aligned with the scatter of the correlation. Further analysis on M31 data is required to see weather the anti-correlation in this regions is extended to whole galaxy or it is only for these 6 regions.

        Studies showed that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}.
        To test that whether anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for neither the clustered data nor all 10 regions.
        Therefore, we conclude that in our sample of studies the high stellar mass does not causes the destruction of PAHs.

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
        According to~\cite{Dim15}, regions 5 and 8 are only two regions in our sample that are not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Thus without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!

@@

       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meanings, we have to mention that, we only used 6 regions to calculate these correlation coefficients.
       Having 6 data points as a sample of the study is not high enough to have a strong conclusion about the PAH in M31.%%% it doesn't sound right:((
        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differs from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, for which their properties are different than the others. %%Again eh!

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One dimensional self-organizing maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible.
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.
%    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
%Clustering
 %   \subsection{Clustering M31 data}

        In order to monitor how the data behaves, we created SOMs with two to fourteen neurons (Fig.~\ref{fig: M31_nets_1d}).
        The $1\times2$ network (Fig.~\ref{fig: M31_net_1by2}) shows how the M31 data can be divided into two broad categories.
        The $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network in which all the regions in M31 are completely separated.
        Since in the higher network sizes, regions have more space to be separated based on their differences,  going from the $1\times2$ to the $1\times14$ network the distance between M31 regions increases, until they are completely separated.

      Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between two right neurons indicates otherwise.

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \cite{Dim15}). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        Similarities with the other regions in the other input values causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

@@

        \begin{figure}
            \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
             }
            \hfill
            \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
            \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
             }
             \hfill
            \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
             }%%% What should I do with this one! It doesn't look good visually
            \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple hexagonal shapes represent the neurons. The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum. The numbers in the plot show the M31 regions located in each neuron.}
            \label{fig: M31_nets_1d}
        \end{figure}

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar areas in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to show more similarities to each other.
        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
       Region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region are much higher than the other regions. %PB: so is the SOM just telling us that the surface brightness is higher in the bulge?
        The region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.

    \subsection{Inside the 2 neuron network}%%% I will find better title for this subsection
        %What is going on in this section
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure}
        \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure}

        %%% what regions' version shows and how it compares with the other one:
        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features are highly correlated with each other. 
        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths, or with most of the other quantities.
        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities show themselves. %PB: need to discuss which one is the outlier and why it is reasonable to remove it

        For the remaining PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity.
        These fluxes correlate with SPIRE emission, but to a lesser extent than for data from all regions.
        Correlations between PAH features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Further analyses show that the absence of correlations between PAH fluxes and SFR, is because of one outlier: Region 6. 
        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\rm TIR}$) reappear.
        Strong anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.

        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
        First, the optical data are not corrected for dust extinction.
        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with amount of dust due to extinction \citep{Calzetti94}.
        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same for \sii~and \oiii~emission.
        Second, is the possible effect of observing apertures.
        If the observed regions are located near the edge of H {\sc II} regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
        On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAH features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAH features' underlying continuum emission is from the H {\sc II} regions.
        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
        The later reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.

        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g][]{Haas02,Bendo08,Calapa14, Lu14,Jones15}, a higher stellar mass decreases PAH emission.
        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, and conclude that the PAH emission traces the old stellar population.
        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in clustered data or in all 10 regions.
      %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
      %It is possible that all the 10 regions in M31 simply aligned with the scatter of the correlation. Further analysis on M31 data is required to see weather the anti-correlation in this regions is extended to whole galaxy or it is only for these 6 regions.

        Some studies have indicated that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}.
        To test that whether anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for either the clustered data or all 10 regions.
        Therefore, we conclude that in our sample,  stellar mass does not cause the destruction of PAHs.

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!

@@

       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to mention that we only used 6 regions to calculate these correlation coefficients.
       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.%%% it doesn't sound right:((
        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties. %%Again eh!

### 2016-07-05 sections/R20.0.tex

    \subsection{Testing networks using M101 observations}
    Another application of SOM for nearby galaxies is to apply the trained networks on the data from other galaxies in order to predict properties of the observed regions in them. %%eh
    Therefore, we generated an SOM using data from M31 that hold in common with M101 data (Fig.~\ref{fig: subset9}a). 
    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs from these two galaxies (For more detail see \cite{Dim15} and \cite{Gordon08}).
    In this SOM, the same as the others, region 10 is separated from other regions in M31.
    Regions 7 and 4 are close to each other with very light colours between their neurons, and the same as the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
    \import{../sections/image_texts/}{subset9.tex}

    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these regions have similar properties.

    Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
    Region 6 in M31 is located near the inner ring of the galaxy (see Fig.~\ref{fig: regions in m31}).
    Both regions have relatively low amount of PAHs emission and medium amount of the SFR regarding the other regions in the galaxy, which makes them very similar regions.

    Region 5 in M31 is in inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region.
    region 8 in M101 is in a spiral arm of the galaxy.
    Relatively low stellar mass, SFR and SPIRE band emission caused these two regions have close distance in the map.
    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties, in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101. 
    These regions all have medium or low amount of PAHs, dust and SFR compare to the rest of them.

    Region 7 in M101 is located in the nucleus of the galaxy and has relatively higher quantities than the other regions.
    This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
    Since the bulge of a spiral galaxy has different environment from its nucleus, region 7 in M101 and region 10 in M31 are not occupied the same neuron in the SOM, and have a medium grey colour between their neurons.

    Region 1 in M101 is located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities than the ones in region 7.
    The lower values for fluxes of the PAH features, and relatively moderate amount of the SFR caused this region places between region 4 and 5 of M31 in the network. 
    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated itself from other regions and located between region 9 and 10 in M31.
    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high amount of fluxes of PAH features. 
    This region also shows a high amount of the SFR and the stellar mass, which describes why the location of region 4 from M101 in the SOM is close to regions 9 and 10 from M31.

    Knowing effect of each data entry on the networks From Section~\ref{sec: subsets}, we can have ideas about that data entry that we do
    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
    We should note that, since we normalized data before using them in the networks, we only see a relative properties of the regions.
    Therefore, we need data from few regions in the galaxy to use this network cannot use these networks to learn about properties of a single region in other galaxies.

>>>>

    \subsection{Testing networks using M101 observations}
    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions. %%eh
    To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs om these two galaxies (For more detail see \cite{Dim15} and \cite{Gordon08}).
    In this SOM, as in the others, region 10 is separated from other regions in M31.
    Regions 7 and 4 are close to each other with very light colours between their neurons, and as in the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
    \import{../sections/image_texts/}{subset9.tex}

    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties. 
    %PB join paragraphs
    Region 2 in M101 is a bright H {\sc II} region located at the end of the one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
    region 6 in M31 is located near the inner star-forming ring (see Fig.~\ref{fig: regions in m31}).
    Both regions have relatively low PAH emission and a median amount of  SFR compared to other regions in the galaxy,  makeing them very similar.

    Region 5 in M31 is in the inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region, while
    region 8 in M101 is in a spiral arm of the galaxy.
    Relatively low stellar mass, SFR and SPIRE band emission caused these two regions to be nearby in the map.
    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties; in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101. 
    These regions all have medium or low PAH emission, dust and SFR compared to the remaining regions.

    Region 7 in M101 is located in the nucleus of the galaxy and has relatively higher values of the quantities than the other regions.
    This region is located in the top right side of the network in Fig.~\ref{fig: subset9},  close to the location of M31 region 10 in the network.
    Since the bulge of a spiral galaxy has a different environment from its nucleus, region 7 in M101 and region 10 in M31 do not occupy the same neuron in the SOM, and have a medium grey colour between their neurons.

    Region 1 in M101 is also located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities compared to region 7.
    The lower values for fluxes of the PAH features and moderate amount of the SFR caused this region to be placed between M31 regions 4 and 5 in the network. 
    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated from other regions and located between M31 regions 9 and 10.
    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high PAH emission. 
    This region also shows a high SFR and stellar mass, explaining why the location of M101 region 4 in the SOM is close to that of M31 regions 9 and 10.

    %PB: this paragraph seems to be unfinished?
    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, we can have ideas about that data entry that we do
    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
    We should note that, since we normalized data before using them in the networks, we only see relative properties of the regions.
    Therefore, we need data from few regions in the galaxy to use this network cannot use these networks to learn about properties of a single region in other galaxies.
